### 2015-04-01 README.Rmd
updated readme

@@

```{r}
get_ids(names="Poa annua", db=c("gbif","eol"), rows=1)
```

@@

```{r}
sci2comm('Helianthus annuus', db='itis')
```

@@

```{r}
comm2sci("black bear")
```

@@

```{r}
as.uid(list("315567","3339","9696"))
```

@@

```{r}
out <- as.uid(c(315567,3339,9696))
(res <- data.frame(out))
```

###

>>>>

Windows users install [Rtools](http://cran.r-project.org/bin/windows/Rtools/) first.

@@

```{r}
get_ids(names="Poa annua", db = "gbif", rows=1)
```

@@

```{r}
sci2comm('Helianthus annuus', db = 'itis')
```

@@

```{r}
comm2sci("black bear", db = "itis")
```

@@

```{r}
as.uid(list("315567", "3339", "9696"))
```

@@

```{r}
out <- as.uid(c(315567, 3339, 9696))
(res <- data.frame(out))
```
